---
title: "Untitled"
author: "Ujang Fahmi"
date: "3/18/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
library(echarts4r)

# data yang beruhba
df <- data.frame(
  year = c(
    rep(2016, 25),
    rep(2017, 25),
    rep(2018, 25),
    rep(2019, 25)
  ),
  x = rnorm(100),
  y = rnorm(100),
  grp = c(
    rep("A", 50),
    rep("B", 50)
  )
) 

df %>%
  group_by(year) %>% 
  e_charts(x, timeline = TRUE) %>% 
  e_scatter(y, symbol_size = 5)
```

